---
title: "Coding Excersise - Lab 1"
author: "Ashley Anderson"
date: "9/5/2019"
output: html_document
---

###Understanding Concepts 

You may work on this with your partner or individually. 

####1. Explain the difference between Git and Github.

\quad Git is a version control system, and Github is online remote cloud that will record all changes and commits made to your projects. 
  
####2. Can Git and Github be used independently? Why don't we do so? Describe the advantages and disadvantages. 

\quad No. Without Git, Github has no way to recieve that changes made to your projects. Without Github, Git cannot record the changes in the cloud, meaning it can't be accessed easily later if needed. We use both together for an easy way to access older versions of our work if needed and to record changes we make to projects. 

####3. What is a repository in Git and how can you create a repository in Git (write out the command(s))?

\quad A repository in Git is basically a storage folder where you store and update your projects. To create a repository in Git, you write "git init" to initialize and create your repository. 

###Coding Excersise
####1. Write code to count the total number of `NA` occurrences in the vector `X =c(47,34,33,65,37,NA,43,NA,11,NA,23,NA)`.

```{r}
x <- c(47,34,33,65,37,NA,43,NA,11,NA,23,NA)
sum(is.na(x))
```


####2. Run the following code: 

```{r}
   age = c(25,30,45,60,12,41)
   smoker = c('T','F','T','F','F','F')
   weight = c(120,137,0,168,91,142)
   example_data = data.frame(age,smoker,weight)
```
   
This code took three vectors (`age`, `smoker`, and `weight`) and binded them together into an `R` object known as a 
`data.frame`. The advantage of `data.frame` is that it can handle vectors of different types. For example, age is a numeric vector but smoker status is a character vector (T or F). We named this `data.frame` as `example_data`. I obviously made a data entry error: someone cannot have 0 weight. The correct weight should be 150 pounds. Write one line of code that can easily correct this using the `[]` syntax. 

```{r}
example_data$weight[which(weight==0)] <- 150
example_data
```


####3. In the following I have two code snippets. Turn these code snippets into functions. Think about what each function does and what you would name it. How many arguments does it need? 

```{r, eval=FALSE}
  mean(is.na(x))

  x / sum(x, na.rm = TRUE)
```

```{r}
mean_fun <- function(x){
  m <- sum(is.na(x))
  m2 <- m/length(x)
  return(m2)
}
mean_fun(x)

fun <- function(x){
  x2 <- x[-which(is.na(x))]
  m <- x/sum(x2)
  return(m)
}
fun(x)

```


####4. Write a function named `both_na()`. This function take two vectors of the same length and returns the number of positions that have an `NA` value in both vectors.

```{r}
x1 <- c(NA,2,3,NA,NA)
y1 <- c(1,NA,3,NA,NA)
na_fun <- function(x,y){
  x <- which(is.na(x))
  y <- which(is.na(y))
  
}
```

